Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-03-25 RR_manuscript/Draft_RR.Rmd
:memo: - edits to RR

As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.

We are closely following the data collection procedure proposed by Parker et al. (Stage 1 in-principle accepted).
The project involves the following five phases:

@@

The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project and a short pre-recorded slide show that summarizes the study and research question (<https://many-speech-analyses.github.io>).
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer to single researcher or small teams as "analysis teams".
Recruitment for this project will commence upon receiving in-principle acceptance; we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).

We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.

Following Parker et al. [@Parker2020], we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient.
The probability $Pr$ that a CrI interval does not include 0 is obtained via the *t*-statistic:

$$t = \frac{\tau^2}{SE(\tau^2)}$$

Assuming that the underlying distribution of effect sizes is normal [@knight2000], the standard error of $\tau^2$ can be calculated with the following formula:

$$SE(\tau^2) = \sqrt{\frac{2\tau^4}{(n-1)}}$$

where $n$ is the sample size.
Given $Pr$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
Inserting $SE(\tau^2)$ into the formula for the *t*-statistic shows that, when $n$ is fixed, *t* (and hence $Pr$) will be the same regardless of $\tau^2$:

$$t = \frac{\tau^2}{SE(\tau^2)} = \frac{\tau^2}{\sqrt{\frac{2\tau^4}{(n-1)}}} = \sqrt{\frac{(n-1)}{2}}$$

In other words, the minimum sample size $n$ needed to exclude 0 from the 95% CrI of $\tau^2$ is invariant regardless of the estimate of heterogeneity $\tau^2$.
When $n = 12$ then $t_{(12-1)} = t_{(11)} = 2.3452$ and $p = 0.0388$, which we consider sufficiently unlikely.

```{r t, eval=FALSE, include=FALSE}
n = 12
df = n - 1
t <- sqrt((df)/2)
pt(t, df, lower.tail = F) * 2
```

@@

The posterior distribution of the population-level intercept $\alpha$ will allow us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \@ref(anares-preds).
Crucially, the posterior distribution of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.

@@

Following Parker et al. (in principle accepted), the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
The SDI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat predictors as species and individual analyses as sites.
For each pair of analyses $(X, Y)$, the SDI will be obtained using the following formula:

>>>>

As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and research-related predictors affect the researchers' final results.

We are closely following the data collection procedure proposed by @Parker2020.
The project involves the following five phases:

@@

The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project and a short pre-recorded slide show that summarizes the study and research question (<https://many-speech-analyses.github.io>).
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer to single researcher or small teams as "analysis teams".
Recruitment for this project will commence upon receiving in-principle acceptance.
As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytical estimate *per se*.
Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, it is not possible for us to establish a well-grounded minimal sample size.
Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.

We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).

All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
Informed consent will be obtained as part of the intake form.

@@

The posterior distribution of the population-level intercept $\alpha$ will allow us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in Section \@ref(anares-preds).
Crucially, the posterior distribution of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.

@@

Following @Parker2020, the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
The SDI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat predictors as species and individual analyses as sites.
For each pair of analyses $(X, Y)$, the SDI will be obtained using the following formula:

### 2021-03-25 RR_manuscript/Draft_RR.tex
:memo: - edits to RR

As outlined in Section \ref{s:operspeech}, researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.

We are closely following the data collection procedure proposed by Parker et al.~(Stage 1 in-principle accepted).
The project involves the following five phases:

@@

The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project and a short pre-recorded slide show that summarizes the study and research question (\url{https://many-speech-analyses.github.io}).
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer to single researcher or small teams as ``analysis teams.''
Recruitment for this project will commence upon receiving in-principle acceptance; we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).

We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.

Following Parker et al. (Parker et al. 2020), we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
We consider a posterior distribution of \(\tau^2\), for which the 95\% credible interval (CrI) does not include 0 as sufficient.
The probability \(Pr\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistic:

\[t = \frac{\tau^2}{SE(\tau^2)}\]

Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the following formula:

\[SE(\tau^2) = \sqrt{\frac{2\tau^4}{(n-1)}}\]

where \(n\) is the sample size.
Given \(Pr\) and \(\tau^2\), we can calculate \(n\) such that \(p < 0.05\).
Inserting \(SE(\tau^2)\) into the formula for the \emph{t}-statistic shows that, when \(n\) is fixed, \emph{t} (and hence \(Pr\)) will be the same regardless of \(\tau^2\):

\[t = \frac{\tau^2}{SE(\tau^2)} = \frac{\tau^2}{\sqrt{\frac{2\tau^4}{(n-1)}}} = \sqrt{\frac{(n-1)}{2}}\]

In other words, the minimum sample size \(n\) needed to exclude 0 from the 95\% CrI of \(\tau^2\) is invariant regardless of the estimate of heterogeneity \(\tau^2\).
When \(n = 12\) then \(t_{(12-1)} = t_{(11)} = 2.3452\) and \(p = 0.0388\), which we consider sufficiently unlikely.

@@

The posterior distribution of the population-level intercept \(\alpha\) will allow us to estimate the range of probable values of the standardized effect size \(\hat{\eta}\).
The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \ref{anares-preds}.
Crucially, the posterior distribution of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.

@@

Following Parker et al.~(in principle accepted), the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice 1945; Sørensen 1948).
The SDI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat predictors as species and individual analyses as sites.
For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:

>>>>

As outlined in Section \ref{s:operspeech}, researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and research-related predictors affect the researchers' final results.

We are closely following the data collection procedure proposed by Parker et al. (2020).
The project involves the following five phases:

@@

The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project and a short pre-recorded slide show that summarizes the study and research question (\url{https://many-speech-analyses.github.io}).
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer to single researcher or small teams as ``analysis teams.''
Recruitment for this project will commence upon receiving in-principle acceptance.
As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytical estimate \emph{per se}.
Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, it is not possible for us to establish a well-grounded minimal sample size.
Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.

We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).

All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
Informed consent will be obtained as part of the intake form.

@@

The posterior distribution of the population-level intercept \(\alpha\) will allow us to estimate the range of probable values of the standardized effect size \(\hat{\eta}\).
The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in Section \ref{anares-preds}.
Crucially, the posterior distribution of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.

@@

Following Parker et al. (2020), the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice 1945; Sørensen 1948).
The SDI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat predictors as species and individual analyses as sites.
For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:
